---
title: "SecretSanta: flexible pipelines for automated prediction of secreted proteins."
author: "Anna Gogleva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**SecretSanta predict** is based on a family of wraper functions around [CBS tools](http://www.cbs.dtu.dk/services/). The wrappers are designed to work together. They produce output in a format recognosible by all of them. This enables easy piping of results between individual predictors and enables creation of custom pipelines (vertical concatenation) and aids comparison of results between several tools (horizontal concatenation).

To speed-up processing of large input fasta files (containing several thousands of sequences) singalp and targetp predictions are automatically run as embarassingly parallel processes when number of input sequences exceedes a certain limit (600 - for signalp; 500 - for targetp).

Majority of the functions could be run in 2 modes: starter - in the case you initiate secretome pipeline with the above tool; and 'piper' - so that the tool expects to see output from other wraper functions.

**SecretSanta annotate**
not implemented yet

**SecretSanta compare**
not implemented yet

**SecretSanta visualise**
not implemented yet

## Installation of external dependencies

For prediction of secreted proteins SecretSanta relies on a set of existing [CBS tools](http://www.cbs.dtu.dk/services/). Please install them and configure according to the listed requirements. Currently R intreface is implemented for the following tools:

\newline

### Tools for prediction of signal peptides and cleavage sites:
- **signalp-2.0** 
    + This version can run under IRIX, IRIX64, Linux, OSF1, SunOS.
    + Download stand alone signalp2.0 http://www.cbs.dtu.dk/cgi-bin/sw_request?signalp+2.0
    + Unpack the archive
    ```{sh eval = FALSE}
    tar -zxvf signalp-2.0.Linux.tar.Z
    cd signalp-2.0
    ```
    + Edit "General settings" at the top of the signalp file. Set value of 'SIGNALP' variable to be path to your signalp2.0 directory. Other variables usually do not require changes. We will not use plotting functions from signalp, so gnuplot, ppmtogif and ghostview are not requred. For more details please check ```signalp-2.0.readme```. 

\newline

- **signalp-3.0** 
    + This version can will run on the most common UNIX platforms.
    + Download stand alone signalp3.0 http://www.cbs.dtu.dk/cgi-bin/sw_request?signalp+3.0
    + Unpack the archive
    ```{sh eval = FALSE}
    tar -zxvf signalp-3.0.Linux.tar.Z
    cd signalp-3.0
    ```
    + Similar to signalp2, edit "General settings" at the top of the signalp file. Set value of 'SIGNALP' variable to be path to your signalp3.0 directory. Other variables usually do not require changes. We will not use plotting functions from signalp, so gnuplot, ppmtogif and ghostview are not requred. For more details please check ```signalp-3.0.readme```.
    
\newline
 
- **signalp-4.1** - the most recent version
    + This version can run under Windows, OS X (Macintosh) and Linux.
    + Download stand alone signalp4.0 http://www.cbs.dtu.dk/cgi-bin/sw_request?signalp+4.0
    + Unpack the archive
    ```{sh eval = FALSE}
    tar -zxvf signalp-4.1.Linux.tar.Z
    cd signalp-4.1
    ```
    + Edit "General settings" at the top of the signalp file. Set values for 'SIGNALP' and 'outputDir' variables.
    For more details please check ```signalp-4.1.readme```.

\newline

### Tools for prediction of protein subcellular localisation:    
    
- **taretp-1.1**
    + tatgetp1.1 will run on the most common UNIX platforms  
    + Download stand alone targetp http://www.cbs.dtu.dk/cgi-bin/nph-sw_request?targetp
    + Unpack the archive:
    ```{sh eval = FALSE}
    tar -zxvf targetp-1.1b.Linux.tar.Z 
    cd targetp-1.1
    ```
    + Edit the paragraph labeled "GENERAL SETTINGS, customise" at the top of the targetp file.
    Set values for 'TARGETP' and 'TMP' variables. Ensure, that the path to targetp does not exceed 60 characters,
    otherwise targetp might fail.

\newline

- **WoLFPsort**
    + Clone WoLFPsort
    ```{sh eval = FALSE}
    git clone https://github.com/fmaguire/WoLFPSort.git
    cd WoLFPSort
    ```
    + Copy the binaries from the appropriate platform specific binary directory ```./bin/binByPlatform/binary-?``` to ```./bin/```
    + For more details please check the ```INSTALL``` file.
    
\newline

### Tools for prediction of transmembrane domains
- **tmhmm-2.0**
    + tmhmm-2.0 will run on the most common UNIX platforms  
    + Download stand alone tmhmm (http://www.cbs.dtu.dk/cgi-bin/nph-sw_request?tmhmm)
    + Upack the archive:
    ```{sh eval = FALSE}
    tar -zxvf tmhmm-2.0c.Linux.tar.gz
    cd tmhmm-2.0c
    ```
    + Set correct path for perl 5.x in the first line of ```bin/tmhmm``` and ```bin/tmhmmformat.pl``` scripts.
    + For more details please check the ```README``` file.
    

\newline

### Checking that all the external dependencies are present and executable in principle:
To do this create a 2-column space-separated text file with listed paths for all the external dependencies. 

```{r, message = FALSE}
library(SecretSanta)
```

```{r, echo = FALSE}
pp <-  suppressMessages(readr::read_delim(system.file("extdata", "santa_paths",
                                                      package="SecretSanta"),
                                          delim = ' ',
                                          col_names = FALSE))
names(pp) <- c('tool', 'path')

```

Sample input file listing paths to external dependencies:
```{r, echo=FALSE}
knitr::kable(pp)
```

To check that all the required dependencies are installed correctly and can be executed in principle, run ```manage_paths``` function. Note, that ```manage_paths``` function is case insensitive and converts all the tool names to the lower case. For CBS tool names please use simple character strings without version numbers. The only exception is signalp - that requires version number in one-digit format.

```{r, echo = TRUE, collapse = TRUE}
santa_paths <- manage_paths(system.file("extdata", "sample_paths", package = "SecretSanta"))
```

## Signalp

- signalp2
- signalp3
- signalp4

In case of large input files SecretSanta runs signalp as an embarassingly parallel process, suitable for clusters.

## Targetp

## TMHMM

## WolfPsort

## Check for terminal ER-retention motifs

## M-slicer

## Building pipelines, simple workflow

## Building pipelines, stringent workflow





Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
