---
title: "SecretSanta: automated prediction of secreted proteins."
author: "Anna Gogleva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

SecretSanta offers a family of wrappers around CBS tools to facilitate automated predicion of secreted proteins.
Implemented S4 class systems restricts output to a particular format, this enables easy piping of results between
multiple tools.

SecretSanta provides an interface to CBS tools, so that you can easily pipe and combine predictions from multiple tools in a single pipeline. 

## Installation of external dependencies

## Signalp

- signalp2
- signalp3
- signalp4

In case of large input files SecretSanta runs signalp as an embarassingly parallel process, suitable for clusters.

## Targetp

## TMHMM

## WolfPsort

## Check for terminal ER-retention motifs

## M-slicer

## Building pipelines, simple workflow

## Building pipelines, stringent workflow





Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
